comgen-outline

### 2017-06-22 paper/appendix-fullModelPosteriors.Rmd
adjust data paths

# Appendix C: Full model posteriors

@@

d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments.csv", sep = ""))

>>>>

# Appendix C: Full model posteriors
```{r}
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
```

@@

d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))

### 2017-06-22 paper/comgen-paper.Rmd
adjust data paths

#### Method
```{r}
d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments.csv", sep = ""))
d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "naturalGenerics-trials-formatted.csv", sep = ""))

>>>>

#### Method
```{r eval = F}
d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))
d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "naturalGenerics-trials-formatted.csv", sep = ""))
